\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-06-19 introduction.tex
first commit
Added the introduction and motivation

\section{Experimental results}
\label{sec:experimental-results}

>>>>

\section{Introduction and motivation}
\label{sec:intr-motiv}

Reactive languages~\cite{gber05,amal10} are a class of programming
languages used for designing and implementing \textit{reactive} systems,
which continuously respond to input from their environment. These
languages have been successfully used in programming a plethora of
systems such as fly by wire in Airbus~\cite{eairbus}, security
surveillance systems~\cite{amal121}, etc. Usually the working
environment of these reactive systems is also real-time. Yet, these
languages do not support describing real-time as first class language
constructs. For example, one cannot describe a simple real-time delay
\texttt{delay 0.2 ms} in these languages. These languages are based on
formal semantics, essential for the formal verification of functional
correctness of the developed programs, but leave non-functional
properties such as timing behavior as an implementation
detail~\cite{ringler00,boldt07}.

These languages only support discrete \textit{logical} clock rather than
a continuous clock. The period of the discrete logical clock (also
referred to as a \textit{logical tick}) is determined by the
responsiveness of the program and as opposed to a discrete
\textit{physical} clock is elastic. Although this timing model has
worked well for these languages in designing discrete systems there is
obviously a need to introduce continuous time since often implementation
models are in the continuous time
domain~\cite{DBLP:journals/pieee/SifakisTY03}.

\input{motivation}

The fundamental contribution of this paper is the inclusion of real-time
constructs in GALS (and its subset synchronous) reactive
languages. Moreover, our contributions can be further refined as
follows:

\begin{enumerate}
\item The real-time is modeled in the $\mathbb{Q}^{>0}$ domain of
  numbers, i.e., non-negative rational numbers.
\item We consider the property of \textit{non maximal-parallelism},
  i.e., we consider scheduling on constrained resources to be an
  integral part of the solution. To our knowledge we are the very first
  to do so.
\item Our solution does not change the functional or timing semantics of
  GALS and its subset synchronous programs, in fact, our solution does
  not require one to change the compiler at all.
\item Our solution gives complete control of under and over
  approximation of real-time to the system designer.
\end{enumerate}

The rest of the paper is arranged as follows...

### 2013-06-19 motivation.tex
separated introduction and motivation
Added the introduction and motivation

\section{Related work}
\label{sec:related-work}

>>>>

\subsection{Motivating Example}
\label{sec:motivating-example}

% system{
%  interface{
%   input signal TOUCH;
%   output signal GREEN_LIGHT;
%   output char channel S;
%   input char channel R;
%  }
\begin{figure}[t!]
% \begin{center}
\begin{minipage}{5cm}
\begin{verbatim}
{ // Clock-domain 1
while(1) {
  trap(TRAP){
   // Abort if user touches the screen
   abort(TOUCH){
    {sustain GREEN_LIGHT;}
    || // synchronous parallel operator
    {
    //exit after any 
    // where from 0.5 to 1 ms.
    /*delay [0.5..1]ms;*/
    exit(TRAP); 
    }
   } do {send S(1);} // Send 1 if touched 
  } do {send S(0);} // Else Send 0
  pause; // only construct to consume time
 }
}
>< // asynchronous operator
{ // Clock-domain 2
  while(1){ receive S;}
  // do something with S
}
\end{verbatim}
\end{minipage}
\caption{An example human reaction time collection system (HRTCS)}
% }
% \end{center}
\label{fig:1}
\end{figure}

Consider a simple machine used to test human reaction time and collect
this data for future research purposes. The machine switches on a green
light on a touch screen for anywhere between \texttt{0.5ms} to
\texttt{1ms}, if the user can touch this green light then she is
successful and an integer \texttt{1} is sent to a data-base server, if
unsuccessful a \texttt{0} is sent instead, this way a database of human
responsiveness can easily be generated.

The SystemJ~\cite{amal10} code for such a system is shown in
Figure~\ref{fig:1}. We use the SystemJ language in this paper first of
all, because being a \textit{Globally Asynchronous Locally Synchronous}
(GALS) language it helps us easily describe a larger class of systems
(like HRTCS in Figure~\ref{fig:1}) compared to purely synchronous
languages like Esterel. Moreover, being a super-set of Esterel, SystemJ
allows us to explore the marriage of real-time and logical time, which
is equally applicable to the synchronous sub-set.

The SystemJ program is divided into two clock-domains, the first
clock-domain continuously displays a green light (\texttt{GREEN\_LIGHT}
signal) on the touch screen sensor and waits for the user to respond. If
the user is able to touch the screen within the specified time of
\texttt{0.5ms} to \texttt{1ms} a positive response is sent to the second
clock-domain, which is interacting with data-base (via CSP style channel
communication via \texttt{S}) server in Java. The synchronous parallel
operator \texttt{||} along with the \texttt{trap-exit} (exception
mechanism) is used to make sure that the green light is switched on for
only a specified delay. The 2 clock-domains are implemented using the
asynchronous parallel \texttt{><} operator. All these constructs are
described in~\cite{amal10}.

This SystemJ example is \textit{incomplete}, the \texttt{delay}
specification, which models the non-deterministic delay between
\texttt{0.5ms} and \texttt{1ms} does not work with the SystemJ compiler!
In fact, there is no way to include such real-time specifications in the
language itself.
